The Effect of Episodic Retrieval on Inhibition in Task Switching

### 2015-11-22 2015/Episodic Retrieval & Inhibition/Manuscript Files/main.tex
added analysis

@@

\subsection{Stimuli \& Apparatus}

\subsection{Procedure}

\subsection{Design}

>>>>

\begin{figure}
\begin{center}
\includegraphics[width = 0.5 \textwidth]{Images/mayrExperiment.pdf}
\caption{Schematic overview of Mayr's (2002) experimental procedure. See text for details.}
\label{fig:mayrExperiment}
\end{center}
\end{figure}

\section{Changes from Mayr's (2002) Experiment}
List the main changes we made in this experiment compared to that of \cite{Mayr2002}.

@@

\subsection{Apparatus \& Stimuli}
Stimuli were presented on an xin. monitor connected to a PC running E-Prime v. 2.0 software. The stimulus display consisted of an 8cm by 8cm square frame. A black circle (diameter = 1cm) served as the trial stimulus. Possible cues were the words ``horizontal'', ``vertical'', or ``diagonal'', and were presented in black font (enter font details here) directly above the stimulus frame. Responses were collected via a 1-ms precise USB keyboard.

\subsection{Procedure}
On each trial a cue was presented above the frame for xxms. After this time, the circle stimulus appeared in one of the four corners of the frame. The cue remained on the screen during stimulus presentation. The task required participants to mentally make a spatial transformation of the stimulus' location according to the rule dictated by the task cue, and to make a spatially-congruent response to this translated location. For example, if the stimulus was in the top-right corner, the participant would need to make a top-left response if the task was ``horizontal'', a bottom-right response if the task was ``vertical'', and a bottom-left response if the task was ``diagonal''. Responses were made on the numerical part of the keyboard, using the ``4'', ``5'', ``1'', and ``2'' keys for top-left, top-right, bottom-left, and bottom-right responses respectively. Participants were asked to respond as quickly and as accurately as possible. Once a response was registered, the frame was cleared for a response--cue interval of xxms, after which time a new cue appeared for the next trial. The cue for the next trial was chosen randomly with the constraint that task repetitions could not occur (cf., Mayr, 2002); the stimulus location was chosen randomly with no constraints on each trial. If participants made an error, the word ``Error!'' appeared in red for xxms above the stimulus frame (in the cue's position).

Participants were presented with xx trials as practice (which could be repeated upon request). The main experiment presented x blocks of x trials.

\subsection{Design}
The experiment manipulated two factors in a fully-related design: \emph{Task Sequence} (n--2 task repetition [ABA] vs. n--2 task switch [CBA]) and \emph{Response Repetition} (n--2 response repetition vs. n-- response switch). The dependent variables were response time (RT) in milliseconds (ms) and percent accuracy (\%).
